---
title: How to write an Manuscript in Rmd for the Journal of Laboratory Medicine

author:
  - Christopher Turk:
      institute: [sc]
  - John Dorian:
      email: jd@sacredheart.tv
      institute: [sc]
      correspondence: false

institute:
  - sc: Sacred Heart Hospital, Hospitalstreet 1, San DiFrangeles, California

documentclass: article
geometry: margin=1in
fontsize: 12pt

output:
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["float"]
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    keep_tex: true
      
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage{bookman}

- \usepackage{lineno}
- \linenumbers

- \usepackage{caption}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
- \usepackage{longtable}

bibliography: zotero_export.bib
csl: vancouver-brackets_jlabmed.csl


---

**Word count:** currently manually

**Number of figures:** 1

**Number of tables:** 1

**Supplementary Material:** no

\newpage

**List of Abbreviations:**

- ABB1: Abbreviation 1
- ABB2: Abbreviation 2
- g: $\gamma$

# Abstract
**Objectives:**
The aim of the work is to establish a programmer-friendly template for publications using open source software.
**Methods:**
Using R, RStudio, pandoc and Latex the creation of this work was straightforward and efficient.
**Results:**
All formatting required for publication could be adhered to without any further manual intervention.
**Conclusions:**
The character set proved to be robust, reliable and visually appealing. 

**Keywords:** publication, latex, rmarkdown

# Introduction

Nowadays, the creation of texts and publications using WYSIWYG programs has become established in many areas of the scientific world.
However, these solutions have considerable disadvantages compared to more sophisticated apporaches, such as those frequently used in the fields of mathematics and physics.
The aim of this work is to establish these techniques in the fields of life science and medicine


# Material and Methods

The typesetting for this manuscript was performed using the programming language R [@r_core_team_r_2023], RStudio, the \texttt{tidyverse} [@wickham_welcome_2019], pandoc and LaTex. 

# Results

All formatting required for publication could be adhered to without any further manual intervention.
Special formatting as shown below is also possible.

- \textcolor{red}{colored text}
- \texttt{typewriter case}, although it is difficult to distinguish from the font used
- greek letters like $\gamma$

# Disucssion

The result of this template is a beautiful PDF that fulfills all the requirements of a professional scientist, as anyone can see.

Although the use of RStudio makes working with this template quite comfortable, an old legend says that true performance is only possible in Emacs Org mode. 

Therefore, we would like to point out the alternative possible use of emacs.

\newpage

# Ethical conduct of research

**Research funding:** None declared.

**Author contributions:** All authors have accepted responsibility for the entire content of this manuscript and
approved its submission.

**Competing interests:** Authors state no conflict of interest.

**Informed consent and ethical approval:** Not necessary for analysis of already published data.

# References

<div id="refs"></div>

\newpage

# Appendix
```{r fig1, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H"}
library(ggplot2)
ggplot(data=iris,mapping=aes(x=Petal.Length,y=Petal.Width,color=Species))+
  geom_point()+
  geom_smooth(method="lm") +
  labs(title = "An example plot as Figure 1")
```

```{r tbl1, echo=FALSE, message=FALSE, warning=FALSE, fig.pos = "H"}
library(tidyverse)
library(kableExtra)

iris %>% head() %>%
  knitr::kable(
  format = "latex",
  align = "l",
  booktabs = TRUE,
  longtable = TRUE,
  linesep = "",
  caption = "\\textbf{Table 1:} An example table. This table is converted to Latex by knittr::kable",
  table.attr = "style='width:0.5\\linewidth;'"
) %>%
  kableExtra::kable_styling(
    font_size = 10,
    position = "center",
    latex_options = c('striped', 'scale_down'),
    stripe_color = "gray!15"
  )
  
```